% ============================================
% RESULT
% ============================================

\begin{frame}{Current Progress -- Verified Run}
    \begin{itemize}
        \item \textbf{Input tested:} Amazon sales CSV with 10,000 rows and 21 columns.
        \item \textbf{Agent 1:} 210,000 cells profiled; 0 missing cells and 0 duplicate rows in the run.
        \item \textbf{Agent 2:} All 21 columns received a semantic schema blueprint and processing policy.
        \item \textbf{Agent 3:} Cleaned CSV, scaling parameters, column ledger, preprocessing log, and quality metrics generated.
        \item \textbf{Agent 4:} Statistics and chart infrastructure executed through the LangGraph pipeline.
    \end{itemize}
\end{frame}

\begin{frame}{Generated Outputs}
    \begin{itemize}
        \item Cleaned dataset exported to \texttt{backend/outputs/cleaned\_data.csv}
        \item Run metadata exported to \texttt{agent\_run\_diagnostics.json}
        \item Correlation heatmap and numeric distribution charts generated as PNG files
        \item Category and payment-method distribution charts generated from the processed data
        \item Reliability metadata records stage confidence, evidence, and decision readiness
    \end{itemize}
\end{frame}

\begin{frame}{Testing and Engineering Progress}
    \begin{itemize}
        \item Focused tests cover semantic-tagging chunking, currency parsing, duplicate consistency, chart overwrite behavior, and pipeline diagnostics.
        \item Chart generation clears stale PNG files before each run to avoid reporting outdated results.
        \item Pipeline errors are accumulated in shared state and conditional routing stops downstream stages when a critical stage fails.
        \item The current backend is reproducible from a defined input path and writes structured diagnostics for inspection.
    \end{itemize}
\end{frame}
