% ============================================
% REFERENCES
% ============================================

\begin{frame}[allowframebreaks]{References}
    \begin{enumerate}
        \scriptsize
        \item Y.~K. Dwivedi, L. Hughes, A.~M. Baabdullah, et al., ``So what if ChatGPT wrote it? Multidisciplinary perspectives on opportunities, challenges and implications of generative conversational AI for research, practice and policy,'' \textit{International Journal of Information Management}, vol. 71, 2023.
        \item OpenAI, ``GPT-4 Technical Report,'' 2024.
        \item M. Sun, R. Han, B. Jiang, H. Qi, D. Sun, Y. Yuan, and J. Huang, ``LAMBDA: A Large Model Based Data Agent,'' \textit{arXiv preprint arXiv:2407.17535}, 2024.
        \item Y.~K. Liu, et al., ``Summary of ChatGPT-Related Research and Perspective Towards the Future of Large Language Models,'' \textit{arXiv:2306.07209}, 2023.
        \item J. Maynez, S. Narayan, B. Bohnet, and R. McDonald, ``On Faithfulness and Factuality in Abstractive Summarization,'' in \textit{Proceedings of ACL}, 2020.
        \item V. Dibia and C. Demiralp, ``Data2Vis: Automatic Generation of Data Visualizations Using Sequence-to-Sequence Recurrent Neural Networks,'' \textit{IEEE Computer Graphics and Applications}, vol. 39, no. 5, pp. 33--46, 2019.
        \item K. Hu, M.~A. Bakker, S. Li, T. Kraska, and C.~A. Hidalgo, ``VizML: A Machine Learning Approach to Visualization Recommendation,'' in \textit{Proceedings of the CHI Conference}, 2019.
        \item D. Moritz, C. Wang, G.~L. Nelson, H. Lin, A.~M. Smith, B. Howe, and J. Heer, ``Formalizing Visualization Design Knowledge as Constraints,'' \textit{IEEE Transactions on Visualization and Computer Graphics}, 2018.
        \item Y. Luo, X. Qin, N. Tang, and G. Li, ``DeepEye: Towards Automatic Data Visualization,'' in \textit{IEEE ICDE}, 2018.
        \item LangChain, ``LangGraph: A Python Library for Building Stateful, Multi-Agent Applications,'' 2024.
        \item Q. Wu, G. Bansal, J. Zhang, et al., ``AutoGen: Enabling Next-Gen LLM Applications via Multi-Agent Conversation Framework,'' 2023.
        \item Z. Ji, et al., ``Survey of Hallucination in Natural Language Generation,'' \textit{ACM Computing Surveys}, 2023.
        \item G. Li, et al., ``CAMEL: Communicative Agents for `Mind' Exploration of Large Language Model Society,'' \textit{arXiv:2303.17760}, 2023.
        \item N. Shinn, et al., ``Reflexion: Language Agents with Verbal Reinforcement Learning,'' \textit{arXiv:2303.11366}, 2023.
        \item D.~P. Kingma and J. Ba, ``Adam: A Method for Stochastic Optimization,'' \textit{ICLR}, 2015.
        \item E.~J. Hu et al., ``LoRA: Low-Rank Adaptation of Large Language Models,'' \textit{ICLR}, 2022.
    \end{enumerate}
\end{frame}
